### 2019-05-31 Writing/draft_highlighted.tex
Updated Abigail's comments

\begin{document}
\[\[\[%Running head
%\begin{flushright}
%Version dated: \today
%\end{flushright}
\bigskip
\noindent RH: Characters correlation
\bigskip
\medskip
\begin{center}
\noindent{\Large \bf Influence of different modes of morphological character correlation on phylogenetic tree inference}
\bigskip

\noindent {\normalsize \sc Thomas Guillerme $^{1,2,*}$, and Martin D. Brazeau $^{2,3}$}\\
\noindent {\small \it 
$^1$ School of Biological Sciences, University of Queensland, St. Lucia, Queensland, Australia.\\
$^2$Imperial College London, Silwood Park Campus, Department of Life Sciences, Buckhurst Road, Ascot SL5 7PY, United Kingdom.\\
$^3$Department of Earth Sciences, Natural History Museum, Cromwell Road, London, SW75BD, United Kingdom.\\}

@@

In this study, we propose a new metric of raw character difference as a proxy for character correlation.
Using thorough simulations, we test the effect of increasing or decreasing character differences on tree topology.
Overall, we found \hl{a negative} effect of reducing character correlations on recovering the correct topology.
However, this effect is less important for matrices with a small number of taxa (25 in our simulations) where \hl{reducing or increasing} character correlation is not more effective EFFECTIVE FOR WHAT? than randomly drawing characters.
Furthermore, in bigger matrices (350 characters), there is a strong effect of the inference method with Bayesian trees being consistently less affected by character correlation than maximum parsimony trees.

@@

The non-independence of large numbers of morphological characters is often cited in anticipation of problems with morphological data \cite[e.g.][]{Davalos01072014, ZouConvergence}.
The assumption of character independence is central to phylogenetic inference methods such as maximum likelihood and maximum parsimony \citep[e.g.][]{joysey1982problems,felsenstein1985phylogenies,lewisa2001,felsenstein2004inferring}.
\hl{This independence is assumed for both molecular and morphological characters} \citep{huelsenbeck1999effect,Davalos01072014,ZouConvergence}.
\hl{However, threel distinctions can be made between the amount and the nature of the correlation.
First, molecular and morphological data often differs in size and in the amount of states analysed (molecular matrices are generally larger with mainly four states - not including missing data or indels - and morphological matrices are smaller with generally two states but sometimes more than ten;}
\citealt{Guillerme2016146}
\hl{).
Second, characters has been suggested to have stronger correlations in morphological data (i.e. ``concentrated'' correlations) \textit{versus} weaker and more ``spread'' correlations in molecular data}
\citep[\hl{i.e. ``diffused'' correlations - though some regions of the genome can be thought as more correlated than others}][]{huelsenbeck1999effect}.
\hl{Furthermore, because of the ``spread'' correlations in molecular data, it can be harder to link the character correlation to a specific biological phenomenon (i.e. changes in morphological states can be more readily linked to a function \textit{cf.} changes in nucleotide states ; see below).}
Before discussing character correlation further, it is important to understand that correlation may manifest itself in at least three distinct ways:

@@

How \hl{do} these \hl{specific} correlation really affect topology?
% In the specific case of discrete morphological characters, how does the reduc phenotypic information and its different sources of correlation is 
% More specifically, how can phylogenetic inference software distinguish between the complex sources of correlation tha
% In other words, how can we distinguish between the complex sources of correlation in phenotype using only discrete morphological characters?
% \cite{parins2017use}
Here we formally assess the effect of discrete character's correlation using simulated data.
We propose a new distance metric to measure the difference between characters (as a proxy for these three sources of correlation as interpreted by the software) and a protocol to modify discrete morphological matrices to increase/decrease WHICH ONE? the overall differences or similarities between characters.
We found that overall, there is a detectable effect of character correlation on topology where \hl{a decrease} in character dependence results in a decrease in the ability to recover the correct topology.
These results, however, vary greatly in magnitude depending on the size of matrix and the inference method used.

Well this is worrying-because it seems like authors could use these results to justify introducing or ignoring character correlations.  It seems like it would be important to test the effect of correlations in uninformative vs informative characters.  Reconstructors wouldn't know whether each character is informative or not, so they would more likely try to avoid it?  But yeah, maybe that would take another year?
\section{Methods}

@@

\subsubsection{Character Difference ($CD$)}
\begin{equation}
    CD_{(x,y)} = \frac{\sum_{i}^{n}\abs{x_{i} - y_{i}}}{n-1}
\end{equation}
%This is not making sense to me right now... I'll ask you about it when you get home. Nope I got it now.
%CD is similar to https://onlinelibrary.wiley.com/doi/full/10.1111/pala.12384 but by character rather than by species

@@

We standardised each character by arbitrarily modifying their character state tokens (or symbols) by order of appearance.
In other words, we replaced all the occurrences of the first token to be $1$, the second to be $2$, etc.
\hl{This procedure allows to compare characters regardless of the significance given to their tokens (following the \textit{xyz} notation in }
\citealt{felsenstein2004inferring}; \hl{as used in} \citealt{Davalos01072014}).
This way, a character \texttt{A = \{2,2,3,0,0,3\}} for six taxa would be standardised as \texttt{A' = \{1,1,2,3,3,2\}}.
Note that in terms of phylogenetic signal, both \texttt{A} and \texttt{A'} are exactly identical (forming three distinct splits in the tree inference process).
When the character difference is null ($0$) it means that characters convey the same phylogenetic signal (i.e. characters are entirely correlated).
When the character difference is maximal ($1$) it means it conveys the greatest difference in phylogenetic signal (i.e. characters are uncorrelated).
It is important to stress that a character difference of $0$ (i.e. the same phylogenetic signal) does not mean the opposite of $1$ (i.e. \textit{not} the opposite phylogenetic signal but the most different number of implied splits) .
For example with three characters \texttt{A = \{0,1,1,1\}}, \texttt{B = \{1,0,0,0\}} and \texttt{C = \{0,1,2,3\}}, $CD_{(A,B)} = 0$ and $CD_{(A,C)} = 1$.
Because the character is continuous and bounded between $(0,1)$, it can be interpreted as the probability of two characters leading to a different set of splits (i.e. a different phylogenetic signal).
%UG FRUSTRATING -A LOT OF MY EDITS HAVE GOTTEN DELETED :(   OH WELL I'LL JUST PUT BACK THE SUPER IMPORTANT ONES. x
%soooo CD_AC = (0+0+1+1)/(4-1) =2/3  right now.   C needs to change to C={0,0,2,3}  then you get (0+1+1+1)/3=1.  I suggest putting the rough calculation in like I demonstrated-because it's a little bit confusing to figure out.

@@

%I can't find Table 2 in this document...

%I strongly suggest that you labelled these figures more on the fig-put less in the legend-give them titles of Robinson Ford or triplet whatever.  Then in the first line of the fig text- you can say "Robinson Ford distance shows the degree of clade conservatism whatever that means... "  so the reader can immediately know the difference between fig 2 and 3.  To label: (1) text on ylab "Normalized tree similarity"- then each row can just be "# taxa" (2) mtext on xlab "Number of characters"  (3)  legend c("more correlated", "less correlated", "randomised") but leave bayesian and parsimony for the fig text.  The goal being to know what the figure says at a glance-the fig text can help clarify
\begin{figure}[!htbp]
\centering
   \includegraphics[width=1\textwidth]{Figures/RF_results_best.pdf}
\caption{\small{Effect of character difference on recovering the ``normal'' topology. The y axis represents the Normalised Tree Similarity using Robinson-Fould distance for matrices with 25, 75 and 150 taxa from top to bottom respectively. The x axis represents the different character difference scenarios and tree inference method with the ``maximised'' character difference in Bayesian (red) and under maximum parsimony (orange), the ``minimised'' character difference in Bayesian (dark green) and under maximum parsimony (light green) and the ``randomised'' character difference in Bayesian (dark blue) and under maximum parsimony (light blue) for matrices of 100, 350 and 1000 characters in the panels from left to right.}}
\label{Fig:RF_results_best}
\end{figure}

@@

The overall amount of character difference in a matrix has an effect of the ability to recover the correct topology when minimising character difference leading to the smallest loss in phylogenetic information (median $NTS_{RF}$ = 0.869 and median $NTS_{Tr}$ = 0.787\hl{; see supplementary materials 3, Table 3}) followed by randomising the characters (median $NTS_{RF}$ = 0.814 and median $NTS_{Tr}$ = 0.791\hl{; see supplementary materials 3, Table 2}) and maximising the character difference (median $NTS_{RF}$ = 0.698 and median $NTS_{Tr}$ = 0.754\hl{; see supplementary materials 3, Table 2}).
There is a significant difference between all scenarios \hl{in terms of clade conservation ($NTS_{RF}$)} (maximising, minimising and randomising; \hl{\textit{p} = 0; Table} \ref{Tab_pooledscenarios_test}) with the highest probability of overlap being between minimising and randomising the character difference (Bhattacharrya Coefficient (BC) = 0.954 for the $NTS_{RF}$; Table \ref{Tab_pooledscenarios_test}) and the lowest probability between maximising and minimising the character difference (BC = 0.848 for the $NTS_{RF}$; Table \ref{Tab_pooledscenarios_test}).
\hl{There is however no difference in terms of taxa displacement ($NTS_{Tr}$) between the three scenarios (with a BC > 0.98 for each comparison - Table}
\ref{Tab_pooledscenarios_test}).  HERE  CAN YOU GIVE A LITTLE MORE INTUITION ON WHAT THE RESULTS MEAN

%maybe this is table 2?  You say "differennce between the pooled scenarios"  I don't remember what you are talking about-maybe describe the pooled scenarios for the forgetful reader.  I have no idea what table 2 is even saying-the table text could use more hand holding explanations.  # same issues with table 3.  I think I personally would've done these stats differently as a multilevel model so that the bonferroni corrections weren't necessary-but I suppose it doesnt fucking matter with p values like that.  However, table 4 is perfect: don't change a thing.

@@

\hl{When looking at the combined effect of each parameter, the ``maximised'', ``minimised'' and ``randomised'' scenarios $NTS_{RF}$ and $NTS_{Tr}$ never overlap ($BC < 0.95$ - supplementary material 3, tables 16 and 17).}
\hl{When comparing the distribution using the Wilcoxon ranked tests, there was no clear differences  between  tree similarity of differening numbers of taxa, characters, tree correlation, or tree construction method for the taxa displacement metric ($NTS_{Tr}$ - supplementary material 3, tables 21 and 22).}
\hl{In terms of clade conservation ($NTS_{RF}$), however, ``maximised'' and ``minimised'' scenarios produced nearly always consistently different topologies using Bayesian inference (apart for the matrices with 25 taxa and 100 and 350 characters and the matrices with 150 taxa and 350 characters) but not using parsimony inference (only the matrices with 75 taxa and 100 or 350 characters produced different $NTS_{RF}$ distributions - supplementary material 3, tables 19 and 20).}
%TODO: [discussion] This can be explained by lower resolution for Bayesian

@@

\subsection{Effect of character differences on topology}
As expected, there is a significant effect of the character difference in the ability to recover the correct topology.   This is only true for the RF method, no?
The character difference metric can be seen as the inverse of character correlation (see Methods above): a high character difference approximates a low level of character correlation and vice versa.
When characters are correlated, one could expect the matrices to convey a strong (but potentially misleading) phylogenetic signal since every character agrees with each other and conversely, when characters are uncorrelated, one could expect them to convey a weaker phylogenetic signal with a high amount of homoplasy.
Intuitively, ONE WOULD HYPOTHESIZE THAT the ``minimised'' character difference scenario to lead to incorrect but consistent trees, the ``maximised'' scenario to lead to poorly resolved once (very homoplasic trees) and the ``randomised'' scenario to perform the best at recovering the correct topology.   I DONT SEE ANY DATA THAT SUPPORTS THIS STATEMENT
\hl{HOWEVER, throughout our simulation, the ``minimised'' character difference scenario (i.e. increased correlation) tendED to result in trees slightly closer to the ``true'' tree and the ``maximised'' character difference scenario (i.e. decreased correlation) led to slightly worst trees (Fig.}
\ref{Fig:RF_results_best}.
\hl{This (WHAT IS THIS?,  CHARACTER CORRELATION?) did not however APPEAR to affect the taxa placement ($NTS_{Tr}$) for which the confidence intervals overlapped too much to be able to discern clear statistical DIFFERENCES (Fig.}
\ref{Fig:Tr_results_best}).
\hl{However this results needs to be contrasted by the fact that}
the trees generated by the ``minimised'' CORRELATION scenario do not appear better resolved (towards any topology) than the other scenarios (see supplementary material 3, \hl{Figs 9, 10 and 11}).
\hl{Furthermore, it is important to note that on average, less characters where duplicated (replaceD) in the ``minimised'' matrices compared to both the ``maximised'' and ``randomised'' matrices   WHY DID THIS HAPPEN?WHY IS IT IMPORTANT ? (supplementary material 3, Figs 4, 5 and 6).
However, (THIS CLAUSE IS CONFUSING AND KIND OF SOUNDS LIKE BULLSHIT ) this change in the amount of replaced characters did not change the way average character differences VARYed across the three transformed matrices: the character differences were always consistently increased (``maximised''), decreased (``minimised'') and maintained at a normal level (``randomised'') for each replicate (supplementary material 3, Figs 1, 2 and 3).
This suggest that character difference can be decreased with a smaller amount of characters replacements than increasing it.}
I SUDDENLY REALLY DONT LIKE THE TERM CHARACTER DIFFERENCES-ITS THE OPPOSITE OF CHARACTER CORRALTION? IT DOESNT SOUND LIKE IT INTUITIVELY. ITS KIND OF CONFUSING TO HAVE SO MANY TERMS MEANING THE SAME THING -MAXIMIZED V MINIMIZED, CHARACTER CORRALATION, CHARACTER DIFFERENCE.  I'M TIRED AND GRUMPY.

@@

Although we measured a significant difference between smaller and larger matrices (\hl{in terms of number of characters, between 100 and 1000 characters - $BC$ $NTS_{RF}=0.914$ and $BC$ $NTS_{Tr}=0.826$}; Tables \ref{Tab_pooledscharacters_test} and \ref{Tab_pooledstaxa_test}),
these differences have to be contrasted with the probability of overlap between the results distributions that are always \hl{very} high between every matrix's size (Bhattacharrya Coefficients $>0.949$ for both the different number of characters and taxa).
This suggests that the overall character difference metric \hl{can be used as a proxy} for character correlation as it is \hl{not directly dependent} on the number of characters analysed.
Regarding the number of taxa, our results suggest that the effect of character correlation on recovering the right topology is independent on the size of the matrix when pooling the data. DID YOU TALK ABOUT POOLING DATA IN THE METHOSA? I'M NOT SURE WHAT YOU ARE REFERING TO.
Furthermore, using the Normalised Tree Similarity metric ($NTS$) accounts for the fact that topological difference is affected by the sheer number of taxa considered (i.e. we corrected for the expected difference when comparing two random trees with the same number of taxa).

\subsection{Effect of character differences on the inference method}
When considering the pooled effect of the tree inference method, we only detected a significant difference between the Bayesian and the maximum parsimony trees in terms of clade conservation but none in terms of taxa placement (both using a Wilcoxon test and the Bhattacharrya Coefficient; Table \ref{Tab_pooledsmethods_test}).
The difference in the ability of each method to recover the ``correct'' topology has been heavily discussed in the last five years with some indications that Bayesian inference will outperform parsimony when analysing discrete morphological characters alone (\citealt{wrightbayesian2014,OReilly20160081,puttick2017uncertain}; although some critics have raised issues with these investigations \citealt{spencerefficacy2013,goloboff2017weighted}).
In this study, it is possible that our simulation protocol for generating the characters (favouring slightly more M$k$-based characters rather than HKY ones) could slightly favour Bayesian inference over maximum parsimony, however, our protocol for selecting matrices \citep[i.e. those with in a $CI>0.25$ in a quick preliminary parsimony search;][]{OReilly20160081} could also favour maximum parsimony analysis.
It was however not the purpose of this study to compare the overall performance of both methods but rather to measure the effect of character correlation on each of those methods separately.

@@

The differences in performance of the BAYESIAN AND PARSIMONY APPROACHES observed here could be due to the inherent mechanisms of each method.
For any given topology $T$ that was obtained from the ``normal'' matrix and a matrix with high homoplasy, both methods will generate scoreS differently:
(1) in parsimony, the topology will probably be given a bad score (one that implies many changes along the tree) and the optimality criterion (favouring the minimum score) will likely discard the (WHICH TREE? TRUE TREE?)tree.
The tree search will thus likely result in a topology island that will not contain the given topology $T$.
(2) in Bayesian inference, the topology will also be given a bad score (i.e. low likelihood) although the high homoplasy can be accommodated in the tree through high evolution rates or/and long branches.
The rate and the branch length being two parameters among others, the score (the likelihood) will change less drastically than for using parsimony.
Furthermore, in Bayesian inference, a reasonable difference in optimality between two topologies (the acceptance) will not necessarily mean that the given topology $T$ will be discarded.
This difference in both mechanisms could explain why, on average, Bayesian inference seems better to recover the ``normal'' topology than maximum parsimony.
\hl{This can be also supported by the fact that Bayesian inference recovered the ``true'' tree topology slightly but consistently better (supplementary materials 3, figures 12, 13, and 14).}

\subsection{Distinction between different character correlations}
Here we mention three different types of character correlations but evolutionary biologists are mainly interested in the intra-organismal and evolutionary correlations (e.g. in evo-devo \citealt{goswami2006morphological}; or in macroevolution \citealt{fitzjohn2014much}).
These two types of correlations can only be studied \textit{a posteriori} with a phylogenetic hypothesis and should not BE used \textit{a priori} as a criterion to select characters.
In other words, intra-organismal and evolutionary correlation should be studied based on an underlying phylogenetic framework making the correlation induced by data collection (i.e. coding correlation) the only type of correlation that can affect the phylogeny \textit{a priori}.
This dichotomy thus creates a trade \hl{off} between: (1) coding fewer characters (stochastically reducing \textit{a priori} correlation) but making the \textit{a posteriori} correlation more dependent on the coding;
and (2) coding more characters (increasing \textit{a priori} dependence) but allowing the \textit{a posteriori} correlation TO BE less dependent on the coding correlations.

>>>>

\begin{document}
%Running head
\begin{flushright}
Version dated: \today
\end{flushright}

\bigskip
\noindent RH: Characters correlation
\bigskip
\medskip
\begin{center}
\noindent{\Large \bf Influence of different modes of morphological character correlation on phylogenetic tree inference}
\bigskip

\noindent {\normalsize \sc Thomas Guillerme$^{1,2,*}$, and Martin D. Brazeau$^{2,3}$}\\
% Abigail I. Pastore$^{1}$
\noindent {\small \it 
$^1$School of Biological Sciences, University of Queensland, St. Lucia, Queensland, Australia.\\
$^2$Imperial College London, Silwood Park Campus, Department of Life Sciences, Buckhurst Road, Ascot SL5 7PY, United Kingdom.\\
$^3$Department of Earth Sciences, Natural History Museum, Cromwell Road, London, SW75BD, United Kingdom.\\}

@@

In this study, we propose a new metric of raw character difference as a proxy for character correlation.
Using thorough simulations, we test the effect of increasing or decreasing character differences on tree topology.
Overall, we found \hl{a negative} effect of reducing character correlations on recovering the correct topology.
However, this effect is less important for matrices with a small number of taxa (25 in our simulations) where \hl{reducing or increasing} character correlation is not more effective \hl{in getting the expected topology} than randomly drawing characters.
Furthermore, in bigger matrices (350 characters), there is a strong effect of the inference method with Bayesian trees being consistently less affected by character correlation than maximum parsimony trees.

@@

The non-independence of large numbers of morphological characters is often cited in anticipation of problems with morphological data \cite[e.g.][]{Davalos01072014, ZouConvergence}.
The assumption of character independence is central to phylogenetic inference methods such as maximum likelihood and maximum parsimony \citep[e.g.][]{joysey1982problems,felsenstein1985phylogenies,lewisa2001,felsenstein2004inferring}.
\hl{This independence is assumed for both molecular and morphological characters} \citep{huelsenbeck1999effect,Davalos01072014,ZouConvergence}.
\hl{However, several distinctions can be made between the amount and the nature of the correlation.
First, molecular and morphological data often differs in size and in the amount of states analysed (molecular matrices are generally larger with mainly four states - not including missing data or indels - and morphological matrices are smaller with generally two states but sometimes more than ten;}
\citealt{Guillerme2016146}
\hl{).
Second, characters has been suggested to have stronger correlations in morphological data (i.e. ``concentrated'' correlations) \textit{versus} weaker and more ``spread'' correlations in molecular data}
\citep[\hl{i.e. ``diffused'' correlations - though some regions of the genome can be thought as more correlated than others}][]{huelsenbeck1999effect}.
\hl{Furthermore, because of the ``spread'' correlations in molecular data, it can be harder to link the character correlation to a specific biological phenomenon (i.e. changes in morphological states can be more readily linked to a function \textit{cf.} changes in nucleotide states ; see below).}
Before discussing character correlation further, it is important to understand that correlation may manifest itself in at least three distinct ways:

@@

How \hl{do} these \hl{specific} correlation really affect topology?
% In the specific case of discrete morphological characters, how does the reduc phenotypic information and its different sources of correlation is 
% More specifically, how can phylogenetic inference software distinguish between the complex sources of correlation tha
% In other words, how can we distinguish between the complex sources of correlation in phenotype using only discrete morphological characters?
% \cite{parins2017use}
Here we formally assess the effect of discrete character's correlation using simulated data.
We propose a new distance metric to measure the difference between characters (as a proxy for these three sources of correlation as interpreted by the software) and a protocol to modify discrete morphological matrices to increase or decrease the overall differences or similarities between characters.
We found that overall, there is a detectable effect of character correlation on topology where \hl{a decrease} in character dependence results in a decrease in the ability to recover the correct topology.
These results, however, vary greatly in magnitude depending on the size of matrix and the inference method used.

%AP Well this is worrying-because it seems like authors could use these results to justify introducing or ignoring character correlations.  It seems like it would be important to test the effect of correlations in uninformative vs informative characters.  Reconstructors wouldn't know whether each character is informative or not, so they would more likely try to avoid it?  But yeah, maybe that would take another year?
\section{Methods}

@@

\subsubsection{Character Difference ($CD$)}
\begin{equation}
    CD_{(x,y)} = \frac{\sum_{i}^{n}\abs{x_{i} - y_{i}}}{n-1}
\end{equation}
%CD is similar to https://onlinelibrary.wiley.com/doi/full/10.1111/pala.12384 but by character rather than by species

@@

We standardised each character by arbitrarily modifying their character state tokens (or symbols) by order of appearance.
In other words, we replaced all the occurrences of the first token to be $1$, the second to be $2$, etc.
\hl{This procedure allows to compare characters regardless of the significance given to their tokens (following the \textit{xyz} notation in }
\citealt{felsenstein2004inferring}; \hl{as used in} \citealt{Davalos01072014}).
This way, a character \texttt{A = \{2,2,3,0,0,3\}} for six taxa would be standardised as \texttt{A' = \{1,1,2,3,3,2\}}.
Note that in terms of phylogenetic signal, both \texttt{A} and \texttt{A'} are exactly identical (forming three distinct splits in the tree inference process).
When the character difference is null ($0$) it means that characters convey the same phylogenetic signal (i.e. characters are entirely correlated).
When the character difference is maximal ($1$) it means it conveys the greatest difference in phylogenetic signal (i.e. characters are uncorrelated).
It is important to stress that a character difference of $0$ (i.e. the same phylogenetic signal) does not mean the opposite of $1$ (i.e. \textit{not} the opposite phylogenetic signal but the most different number of implied splits) .
For example with three characters \texttt{A = \{0,1,1,1\}}, \texttt{B = \{1,0,0,0\}} and \texttt{C = \{0,0,1,2\}}, $CD_{(A,B)} = 0$ and $CD_{(A,C)} = 1$ \hl{$CD_{(A,B)} = (0+0+0+0)/(4-1) = 0$ and $CD_{(A,C)} = (0+1+1+1)/(4-1) = 1$}.
Because the character is continuous and bounded between $(0,1)$, it can be interpreted as the probability of two characters leading to a different set of splits (i.e. a different phylogenetic signal).

@@

%TODO: I strongly suggest that you labelled these figures more on the fig-put less in the legend-give them titles of Robinson Ford or triplet whatever.  Then in the first line of the fig text- you can say "Robinson Ford distance shows the degree of clade conservatism whatever that means... "  so the reader can immediately know the difference between fig 2 and 3.  To label: (1) text on ylab "Normalized tree similarity"- then each row can just be "# taxa" (2) mtext on xlab "Number of characters"  (3)  legend c("more correlated", "less correlated", "randomised") but leave bayesian and parsimony for the fig text.  The goal being to know what the figure says at a glance-the fig text can help clarify

\begin{figure}[!htbp]
\centering
   \includegraphics[width=1\textwidth]{Figures/RF_results_best.pdf}
\caption{\small{Effect of character difference on recovering the ``normal'' topology. The y axis represents the Normalised Tree Similarity using Robinson-Fould distance for matrices with 25, 75 and 150 taxa from top to bottom respectively. The x axis represents the different character difference scenarios and tree inference method with the ``maximised'' character difference in Bayesian (red) and under maximum parsimony (orange), the ``minimised'' character difference in Bayesian (dark green) and under maximum parsimony (light green) and the ``randomised'' character difference in Bayesian (dark blue) and under maximum parsimony (light blue) for matrices of 100, 350 and 1000 characters in the panels from left to right.}}
\label{Fig:RF_results_best}
\end{figure}

@@

The overall amount of character difference in a matrix has an effect of the ability to recover the correct topology when minimising character difference leading to the smallest loss in phylogenetic information (median $NTS_{RF}$ = 0.869 and median $NTS_{Tr}$ = 0.787\hl{; see supplementary materials 3, Table 3}) followed by randomising the characters (median $NTS_{RF}$ = 0.814 and median $NTS_{Tr}$ = 0.791\hl{; see supplementary materials 3, Table 2}) and maximising the character difference (median $NTS_{RF}$ = 0.698 and median $NTS_{Tr}$ = 0.754\hl{; see supplementary materials 3, Table 2}).
There is a significant difference between all scenarios \hl{in terms of clade conservation ($NTS_{RF}$)} (maximising, minimising and randomising; \hl{\textit{p} = 0; Table} \ref{Tab_pooledscenarios_test}) with the highest probability of overlap being between minimising and randomising the character difference (Bhattacharrya Coefficient (BC) = 0.954 for the $NTS_{RF}$; Table \ref{Tab_pooledscenarios_test}) and the lowest probability between maximising and minimising the character difference (BC = 0.848 for the $NTS_{RF}$; Table \ref{Tab_pooledscenarios_test}).
\hl{There is however no difference in terms of taxa displacement ($NTS_{Tr}$) between the three scenarios (with a BC > 0.98 for each comparison - Table}
\ref{Tab_pooledscenarios_test}).  %AB: TODO: HERE  CAN YOU GIVE A LITTLE MORE INTUITION ON WHAT THE RESULTS MEAN

%TODO: maybe this is table 2?  You say "differennce between the pooled scenarios"  I don't remember what you are talking about-maybe describe the pooled scenarios for the forgetful reader.  I have no idea what table 2 is even saying-the table text could use more hand holding explanations.  # same issues with table 3.  I think I personally would've done these stats differently as a multilevel model so that the bonferroni corrections weren't necessary-but I suppose it doesnt fucking matter with p values like that.  However, table 4 is perfect: don't change a thing.

@@

\hl{When looking at the combined effect of each parameter, the ``maximised'', ``minimised'' and ``randomised'' scenarios $NTS_{RF}$ and $NTS_{Tr}$ never overlap ($BC < 0.95$ - supplementary material 3, tables 16 and 17).}
\hl{When comparing the distribution using the Wilcoxon ranked tests, there was no clear differences  between  tree similarity of differening numbers of taxa, characters, tree correlation, or tree inference method for the taxa displacement metric ($NTS_{Tr}$ - supplementary material 3, tables 21 and 22).}
\hl{In terms of clade conservation ($NTS_{RF}$), however, ``maximised'' and ``minimised'' scenarios produced nearly always consistently different topologies using Bayesian inference (apart for the matrices with 25 taxa and 100 and 350 characters and the matrices with 150 taxa and 350 characters) but not using parsimony inference (only the matrices with 75 taxa and 100 or 350 characters produced different $NTS_{RF}$ distributions - supplementary material 3, tables 19 and 20).}

@@

\subsection{Effect of character differences on topology}
As expected, there is a significant effect of the character difference in the ability to recover the correct topology.
%AB: This is only true for the RF method, no?
The character difference metric can be seen as the inverse of character correlation (see Methods above): a high character difference approximates a low level of character correlation and vice versa.
When characters are correlated, one could expect the matrices to convey a strong (but potentially misleading) phylogenetic signal since every character agrees with each other and conversely, when characters are uncorrelated, one could expect them to convey a weaker phylogenetic signal with a high amount of homoplasy.
Intuitively, one would hypothesise that the ``minimised'' character difference scenario to lead to incorrect but consistent trees, the ``maximised'' scenario to lead to poorly resolved once (very homoplasic trees) and the ``randomised'' scenario to perform the best at recovering the correct topology. 
%AB: TODO: I DONT SEE ANY DATA THAT SUPPORTS THIS STATEMENT
\hl{However, throughout our simulation, the ``minimised'' character difference scenario (i.e. increased correlation) tended to result in trees slightly closer to the ``true'' tree and the ``maximised'' character difference scenario (i.e. decreased correlation) led to slightly worst trees (Fig.}
\ref{Fig:RF_results_best}.
\hl{This
%AB: TODO (WHAT IS THIS?,  CHARACTER CORRELATION?)
did not however appear to affect the taxa placement ($NTS_{Tr}$) for which the confidence intervals overlapped too much to be able to discern clear statistical differences (Fig.}
\ref{Fig:Tr_results_best}).
\hl{However this results needs to be contrasted by the fact that}
the trees generated by the ``minimised'' correlation scenario do not appear better resolved (towards any topology) than the other scenarios (see supplementary material 3, \hl{Figs 9, 10 and 11}).
\hl{Furthermore, it is important to note that on average, less characters where duplicated (replaced) in the ``minimised'' matrices compared to both the ``maximised'' and ``randomised'' matrices (supplementary material 3, Figs 4, 5 and 6).
%AB: TODO:  WHY DID THIS HAPPEN?WHY IS IT IMPORTANT ? 
However,
%AB: TODO (THIS CLAUSE IS CONFUSING AND KIND OF SOUNDS LIKE BULLSHIT )
this change in the amount of replaced characters did not change the way average character differences varyed across the three transformed matrices: the character differences were always consistently increased (``maximised''), decreased (``minimised'') and maintained at a normal level (``randomised'') for each replicate (supplementary material 3, Figs 1, 2 and 3).
This suggest that character difference can be decreased with a smaller amount of characters replacements than increasing it.}
%AB: TODO: I SUDDENLY REALLY DONT LIKE THE TERM CHARACTER DIFFERENCES-ITS THE OPPOSITE OF CHARACTER CORRALTION? IT DOESNT SOUND LIKE IT INTUITIVELY. ITS KIND OF CONFUSING TO HAVE SO MANY TERMS MEANING THE SAME THING -MAXIMIZED V MINIMIZED, CHARACTER CORRALATION, CHARACTER DIFFERENCE.  I'M TIRED AND GRUMPY.

@@

Although we measured a significant difference between smaller and larger matrices (\hl{in terms of number of characters, between 100 and 1000 characters - $BC$ $NTS_{RF}=0.914$ and $BC$ $NTS_{Tr}=0.826$}; Tables \ref{Tab_pooledscharacters_test} and \ref{Tab_pooledstaxa_test}),
these differences have to be contrasted with the probability of overlap between the results distributions that are always \hl{very} high between every matrix's size (Bhattacharrya Coefficients $>0.949$ for both the different number of characters and taxa).
This suggests that the overall character difference metric \hl{can be used as a proxy} for character correlation as it is \hl{not directly dependent} on the number of characters analysed.
Regarding the number of taxa, our results suggest that the effect of character correlation on recovering the right topology is independent on the size of the matrix when pooling the data.
%AB: TODO: DID YOU TALK ABOUT POOLING DATA IN THE METHOSA? I'M NOT SURE WHAT YOU ARE REFERING TO.
Furthermore, using the Normalised Tree Similarity metric ($NTS$) accounts for the fact that topological difference is affected by the sheer number of taxa considered (i.e. we corrected for the expected difference when comparing two random trees with the same number of taxa).

\subsection{Effect of character differences on the inference method}
When considering the pooled effect of the tree inference method, we only detected a significant difference between the Bayesian and the maximum parsimony trees in terms of clade conservation but none in terms of taxa placement (both using a Wilcoxon test and the Bhattacharrya Coefficient; Table \ref{Tab_pooledsmethods_test}).
The difference in the ability of each method to recover the ``correct'' topology has been heavily discussed in the last five years with some indications that Bayesian inference will outperform parsimony when analysing discrete morphological characters alone (\citealt{wrightbayesian2014,OReilly20160081,puttick2017uncertain}; although some critics have raised issues with these investigations \citealt{spencerefficacy2013,goloboff2017weighted}).
In this study, it is possible that our simulation protocol for generating the characters (favouring slightly more M$k$-based characters rather than HKY ones) could slightly favour Bayesian inference over maximum parsimony, however, our protocol for selecting matrices \citep[i.e. those with in a $CI>0.26$ in a quick preliminary parsimony search;][]{OReilly20160081} could also favour maximum parsimony analysis.
It was however not the purpose of this study to compare the overall performance of both methods but rather to measure the effect of character correlation on each of those methods separately.

@@

The differences in performance of the Bayesian and parsimony approaches observed here could be due to the inherent mechanisms of each method.
For any given topology $T$ that was obtained from the ``normal'' matrix and a matrix with high homoplasy, both methods will generate scores differently:
(1) in parsimony, the topology will probably be given a bad score (one that implies many changes along the tree) and the optimality criterion (favouring the minimum score) will likely discard the tree.
%AB: TODO: (WHICH TREE? TRUE TREE?)
The tree search will thus likely result in a topology island that will not contain the given topology $T$.
(2) in Bayesian inference, the topology will also be given a bad score (i.e. low likelihood) although the high homoplasy can be accommodated in the tree through high evolution rates or/and long branches.
The rate and the branch length being two parameters among others, the score (the likelihood) will change less drastically than for using parsimony.
Furthermore, in Bayesian inference, a reasonable difference in optimality between two topologies (the acceptance) will not necessarily mean that the given topology $T$ will be discarded.
This difference in both mechanisms could explain why, on average, Bayesian inference seems better to recover the ``normal'' topology than maximum parsimony.
\hl{This can be also supported by the fact that Bayesian inference recovered the ``true'' tree topology slightly but consistently better (supplementary materials 3, figures 12, 13, and 14).}

\subsection{Distinction between different character correlations}
Here we mention three different types of character correlations but evolutionary biologists are mainly interested in the intra-organismal and evolutionary correlations (e.g. in evo-devo \citealt{goswami2006morphological}; or in macroevolution \citealt{fitzjohn2014much}).
These two types of correlations can only be studied \textit{a posteriori} with a phylogenetic hypothesis and should not be used \textit{a priori} as a criterion to select characters.
In other words, intra-organismal and evolutionary correlation should be studied based on an underlying phylogenetic framework making the correlation induced by data collection (i.e. coding correlation) the only type of correlation that can affect the phylogeny \textit{a priori}.
This dichotomy thus creates a trade \hl{off} between: (1) coding fewer characters (stochastically reducing \textit{a priori} correlation) but making the \textit{a posteriori} correlation more dependent on the coding;
and (2) coding more characters (increasing \textit{a priori} dependence) but allowing the \textit{a posteriori} correlation to be less dependent on the coding correlations.

It is important to note that the two other sources of character correlation could also be present in our simulations although they were not explicitly modelled:
(1) evolutionary correlation is implied by simulating the characters based on Birth-Death trees;
and (2) intra-organismal correlation could also be present in the matrices for those characters randomly simulated but sharing similar evolutionary simulation regimes (i.e. creating ``modules'' of characters).
However, the effect of these sources of correlation was out of the scope of this study and would have required \textit{a posteriori} changes to the matrices.% which are - when using empirical data - at best bad practice and at worst dishonest. AB: TODO: I DONT  REALLY UNDERSTAND
